\LARGE \bf Imposing a Weight Norm Constraint for Neuro–Adaptive Control

### 2025-03-22 manuscript.tex
fix regarding revision comments and new table style

Consider an uncertain Euler‒Lagrange system modeled as
\begin{equation}
    \mm M\ddq + \mm V_m\dq + \mm F + \mm G + \mv\tau_d
    =
    \mv\tau 
    \label{eq. system dynamics 1}
\end{equation}
where $\q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M :=\mm M(\q)\in\mathbb{R}^{n\times n}$, $\mm V_m:= \mm V_m(\q,\dq)\in\mathbb{R}^{n\times n}$, and $\mm G:=\mm G(\q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F:=\mm F(\dq)\in\mathbb{R}^{n}$ denotes the external force.
Using the user-designed matrices $\widehat{\mm M}>0,\widehat{\mm V_m}$ and $\widehat{\mm G}$, \eqref{eq. system dynamics 1} can be represented as 
\begin{equation}
    \widehat{\mm M}\ddq+\widehat{\mm V_m}\dq+\widehat{\mm G} = \mv \tau + \mv f(\q,\dq,\ddq)
    \label{eq. system dynamics 2}
\end{equation}
where $\mv f(\q,\dq,\ddq) := -(\mm M-\widehat{\mm M})\ddq-(\mm V_m-\widehat{\mm V_m})\dq -(\mm G-\widehat{\mm G}) -\mm F$ denotes the residual unknown term.

@@

The backstepping control-based approach is utilized to generate a reference signal $\mv z^*:= -{k_q}\tilde {\q}+\dq_d$ for $\mv {z}:= \dq$, where $\tilde {\q}:= \mv {q} - \qd$ and $k_q\in\R_{>0}$.
The desired stabilizing controller can be designed as follows:
\begin{equation}
    \mv \tau^* = 
    -\widehat{\mm M}\cdot ({k_z}\tilde {\mv z})
    + 
        ( 
            -\widehat{\mm M}\tilde {\q}
            +
            \widehat{\mm V_m}{\mv z}
            +
            \widehat{\mm G}
            -
            \mv f
            +
            \widehat{\mm M} \dot {\mv z}^*
        )
    \label{eq. desired control}
\end{equation}
where $\tilde {\mv z}:= \mv z-\mv z^*$ and $k_z\in\R_{>0}$.
Note that the desired controller cannot be realized because of $\mv f$.

To approximate the desired controller, an NN is utilized.
\MSRY{
    Even though the DNNs have a higher approximation capability than the SHLNNs \cite{Rolnick:2017aa}, here, the SHLNN is utilized for simplicity and low computational complexity.
}
The NN with a single hidden layer is represented as 
\begin{equation}
    \NN({\q_{NN}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{NN}})
\end{equation}
where ${\q_{NN}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denote the total weight vector, where $\Xi_i=(l_i+1)\cdot l_{i+1}$ and $\Xi=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.

Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\wth^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\q_{NN}}\in\Omega_{NN}} \allowbreak \norm{\NN({\q_{NN}};\wth^*) - \mv \tau^*}=\epsilon<\infty$ \cite{Cybenko:1989aa}.
The ideal weight vector $\wth^*$ is typically assumed to be bounded.
Then, using the estimated weight vector $\estwth=(\estwth_1^\top ,\estwth_0^\top )^\top $ of $\wth^*=(\wth_1^{*\top},\wth_0^{*\top})^\top $, the desired controller $\mv \tau^*\approx -\NN(\q_{NN};\wth^*)-\mv\epsilon$ with bounded approximation error $\mv \epsilon\in\R^2$, can be approximated as follows:
\begin{equation}
    \mv \tau := -\NN({\q_{NN}};\estwth)
    .
    \label{eq. control law}
\end{equation}
For further sections, let $\idealNN:=\NN({\q_{NN}};\idealwth)$ and $\idealact :=\act({\idealwV}_0^{\top}{\q_{NN}})$, and let $\estNN:={\NN}({\q_{NN}};\estwth)$, $\estact :=\act(\estwV_0^{\top}{\q_{NN}})$ and $\estact' := \pptfrac{\estact}{\estwV_0^\top \q_{NN}}$.

Using \eqref{eq. system dynamics 2}, \eqref{eq. desired control}, and \eqref{eq. control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi:=(\tilde {\q}^\top ,\tilde {\mv z}^\top)^\top \in\R^{2n}$ as follows:
\begin{equation}
    \dot{\mv \xi} 
    = 
    \mm A_\xi{\mv \xi}+\mm B_\xi(\NN^*-\estNN+\mv\epsilon)
\end{equation}
and 
\begin{equation}
    \mm A_\xi := 
    \begin{bmatrix}
        -{k_q} \mm I_{n} &\mm I_{n}
        \\
        -\mm I_{n}& -{k_z} \mm I_{n}
    \end{bmatrix}
    ,\ 
    \mm B_\xi := 
    \begin{bmatrix}
        \mm 0_{n\times n}\\\widehat{\mm M}^{-1}
    \end{bmatrix}.
\end{equation}

@@

\MSRY{
    As discussed in Section \ref{sec:intro}, the boundedness of the weights should be addressed to prevent excessively large control inputs and system instability.
}
For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ i\in\{0,1\}$.
The control problem can be reformulated into a constrained optimization problem as follows:
\begin{equation}
    \begin{matrix}
        \min_{{\estwth}} \ J(\mv \xi;{\estwth})
        :=
        \tfrac{1}{2}
        \mv \xi^\top \mm \Lambda \mv \xi
        \\ \\
        \begin{aligned}
        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal I 
        = 
        \{\theta_0,\theta_1\}
        ,
        \end{aligned}
    \end{matrix}
\end{equation}
where $\mm \Lambda=\mm \Lambda^\top >0$ denotes the weighting matrix.
In this optimization problem, $\mv \xi$ is considered a predefined parameter.
The corresponding Lagrangian function is defined as
\begin{equation}
    L(
        \mv \xi,
        {\estwth},
        [\lambda_j]_{j\in\mathcal I}
    )
    := 
    J(\mv \xi;{\estwth})
    +
    \textstyle\sum_{j\in\mathcal I} \lambda_jc_j({\estwth})
    .
\end{equation}
% where $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
To solve the dual problem $\min_{{\estwth}} \max_{[\lambda_j]_{j\in\mathcal I}}  L$, the adaptation law is derived as follows:
\begin{subequations}
    \begin{align}
            \ddtt {{\estwth}}
            &
            =
            -\alpha 
            \pptfrac{L}{{\estwth}}
            =-\alpha 
            \left(
                \pptfrac{J}{{\estwth}}
                +
                \textstyle\sum_{j\in\mathcal{I}}
                \lambda_j 
                \pptfrac{c_j}{\estwth}
            \right),
        \label{eq. adaptation law th}
            \\
            \ddtt\lambda_j
            & 
            = 
            \beta_j
            \pptfrac{L}{\lambda_j} 
            = 
            \beta_j c_j ,
            \quad\quad\quad\quad      \      
            \forall j\in\mathcal I,
        \label{eq. adaptation law L}
            \\
            \lambda_j 
            & 
            = 
            \max(\lambda_j,0) ,
        \label{eq. adaptation law L max}
    \end{align}
    \label{eq. adaptation laws}
\end{subequations}
where arguments of $L$ are suppressed for brevity, and $\alpha\in\R_{>0}$ and $\beta_j\in\R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
\color{red}
% The Eq.~\eqref{eq. adaptation law L max} is analog to using an active set $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ in constrained optimization theory which excludes terms of satisfied constraints in adaptation law.
\color{black}

@@

The dynamics of $\mv \xi$ can be represented as
\begin{equation}    
    \ddtt {\mv\xi} = \mm A_\xi\mv \xi +\mm B_\xi
    (
        -\estwV_1^\top \estact+\mv w(t)
    )
\end{equation}
where $\mv w(t):= {\idealwV}_1^{\top}\idealact+\mv \epsilon$ is a lumped residual term, which is bounded as $\norm{\mv  w(t)}\le \bar w< 0$ since $\norm{\idealwth_1},\norm{\idealact}$ and $\norm{\mv\epsilon}$ are bounded.
The dynamics of ${\mm \eta}_1$ and ${\estwth}_1$ are represented as
\begin{equation}
    \begin{aligned}
        \ddtt{\mm \eta}_1 =
        & 
        \mm A_\xi {\mm \eta}_1 -\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )
        ,
        \\
        \ddtt{{\estwth}}_1 =
        & -\alpha 
        (
            {\mm \eta}_1^\top 
            \mm \Lambda
            \mv\xi
            +
            2\lambda_{\theta_1} {\estwth}_1
        )
        .
    \end{aligned} 
\end{equation}
According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $-\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )$ is bounded.

@@

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{System model parameters.}
    \centering
    \begin{tabular}{|c||c|c|c|c|}
    \hline
    Symbol & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline 
    $m_1, m_2$ & Mass of link    & 23.902 (kg) & 3.88 (kg) \\
    \hline
    $l_1, l_2$  & Length of link   & 0.45 (m) & 0.45 (m) \\
    \hline
    $l_{c1}, l_{c2}$ & COM of link  & 0.091 (m) & 0.048 (m) \\
    \hline
    $\theta_1, b_2$   & Viscous coefficient  &  2.288 (Nms) & 0.172 (Nms) \\
    \hline
    $f_{c1}, f_{c2}$  & Friction coefficient &  7.17 (Nm) & 1.734 (Nm) \\
    \hline
    \end{tabular}
    \label{table: system parameters}
\end{table}

@@

The control laws of all three controllers were the same as those defined in \eqref{eq. control law}.
The adaptation law of NAC-L2 is derived by adding the squared weight term $\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$ to the objective function such that $J_{L_2} = J+\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$, where $\lambda\in\R_{>0}$ denotes the $L_2$ coefficient.
The adaptation law obtained via the gradient descent method is subsequently adjusted by adding a stabilizing term $-\alpha\lambda{\estwth}$ as follows:
\begin{equation} 
    \ddtt{{\estwth}} = 
    \pptfrac{J_{L_2}}{\estwth}
    =-\alpha
    \left(
        \pptfrac{J}{\estwth}
        +
        \lambda{\estwth}
    \right)
    .
    \label{eq. adap L2}
\end{equation}
Note that this adaptation law derived based on $L_2$-regularization method in deep learning is inherently the same as the $\sigma$-modification in adaptive control theory, which adds the term $-\alpha\sigma{\estwth}$, where $\sigma\in\R_{>0}$.
For NAC-eMod, similar to the $\sigma$-modification, the stabilizing function $-\alpha\rho\norm{\tilde{\mv z}}{\estwth}$ is added to the adaptation law as follows:
\begin{equation}
    \ddtt{{\estwth}} = -\alpha
    \left(
        \pptfrac{J}{\estwth}
        +
        \rho\norm{\tilde {\mv z}}{\estwth}
    \right)
    \label{eq. adap eMod}
\end{equation}
where $\rho\in\R_{>0}$ denotes the $\epsilon$-modification coefficient.
By $\norm{\tilde {\mv z}}$, the stabilizing function proportionally increases as the tracking error $\tilde {\mv z}$ increases.
Therefore, the adaptation attempts to reduce the tracking error mainly without the effect of the stabilizing function if the tracking error is sufficiently regulated.
The adaptation law of NAC-CO is presented in \eqref{eq. adaptation laws}.
Owing to the stabilizing functions, the weights of NAC-L2 and NAC-eMod are biased since the stabilizing functions drive the weights toward the origin.

All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\widehat{\mm M}=I_2$ and $\mm \Lambda=\text{diag}([5,1,15,15])$.
The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
\MSRY{
    The validity of the selected number of nodes were demonstrated through experiments 
}
The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{NN}=[\qd^\top ,1]^\top $.
For NAC-CO, the parameters of the weight norm constraints were set as $\bar\theta_0=10$ and $\bar\theta_1=20$.
The sampling time of the simulation and the simulation termination time were set to $T_s=100\ \mu\mathrm{s}$ and $T=10\ \mathrm{s}$, respectively.

@@

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Quantitative comparison of square root of tracking ISE.}
    \centering
    \begin{tabular}{|c||c|c|c|}
    \hline
     & \textbf{NAC-L2} & \textbf{NAC-eMod} & \textbf{NAC-CO} (proposed) 
     \\
    \hline 
    Maximum         & $11.1753$e-3 & $0.5603$e-3 & $0.3439$e-3 \\
    \hline
    % Upper quartile  & $1.7284$e-3 & $0.5566$e-3 & $0.3261$e-3 \\
    % \hline
    Median          & $0.5898$e-3 & $0.5519$e-3 & $0.3240$e-3 \\
    \hline
    % Lower quartile  & $0.5533$e-3 & $0.5470$e-3 & $0.3238$e-3 \\
    % \hline
    Minimum         & $0.5434$e-3 & $0.5434$e-3 & $0.3235$e-3 \\
    \hline
    \end{tabular}
    \label{table: error norm}
\end{table}

>>>>

Consider an uncertain Euler‒Lagrange system modeled as
\begin{equation}
    \mm M\ddq + \mm V_m\dq+ \mm G + \mm F 
    =
    \mv\tau 
    ,
    \label{eq. system dynamics 1}
\end{equation}
where $\q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M :=\mm M(\q)\in\mathbb{R}^{n\times n}$, $\mm V_m:= \mm V_m(\q,\dq)\in\mathbb{R}^{n\times n}$, and $\mm G:=\mm G(\q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F:=\mm F(\dq)\in\mathbb{R}^{n}$ denotes the external force.
Using the user-designed matrices $\widehat{\mm M}>0,\widehat{\mm V_m}$ and $\widehat{\mm G}$, \eqref{eq. system dynamics 1} can be represented as 
\begin{equation}
    \widehat{\mm M}\ddq+\widehat{\mm V_m}\dq+\widehat{\mm G} = \mv \tau + \mv f(\q,\dq,\ddq)
    ,
    \label{eq. system dynamics 2}
\end{equation}
where $\mv f(\q,\dq,\ddq) := -(\mm M-\widehat{\mm M})\ddq-(\mm V_m-\widehat{\mm V_m})\dq -(\mm G-\widehat{\mm G}) -\mm F$ denotes the residual unknown term.

@@

The backstepping control-based approach is utilized to generate a reference signal $\mv z^*:= -{k_q}\tilde {\q}+\dq_d$ for $\mv {z}:= \dq$, where $\tilde {\q}:= \mv {q} - \qd$ and $k_q\in\R_{>0}$.
The desired stabilizing controller can be designed as follows:
\begin{equation}
    \mv \tau^* = 
    -\widehat{\mm M}\cdot ({k_z}\tilde {\mv z})
    + 
    ( 
        -\widehat{\mm M}\tilde {\q}
        +
        \widehat{\mm V_m}{\mv z}
        +
        \widehat{\mm G}
        -
        \mv f
        +
        \widehat{\mm M} \dot {\mv z}^*
    ) 
    ,
    \label{eq. desired control}
\end{equation}
where $\tilde {\mv z}:= \mv z-\mv z^*$ and $k_z\in\R_{>0}$.
Note that the desired controller cannot be realized because of $\mv f$.

To approximate the desired controller, an NN is utilized.
\color{red}
    Even though the DNNs have a higher approximation capability than the SHLNNs \cite{Rolnick:2018aa}, here, the SHLNN is utilized for simplicity and low computational complexity.
\color{black}
The NN with a single hidden layer is represented as 
\begin{equation}
    \NN({\q_{NN}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{NN}})
    ,
\end{equation}
where ${\q_{NN}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denote the total weight vector, where $\Xi_i=(l_i+1)\cdot l_{i+1}$ and $\Xi=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.

Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\wth^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\q_{NN}}\in\Omega_{NN}} \allowbreak \norm{\NN({\q_{NN}};\wth^*) - \mv \tau^*}=\epsilon<\infty$ \cite{Cybenko:1989aa}.
The ideal weight vector $\wth^*$ is typically assumed to be bounded.
Then, using the estimated weight vector $\estwth=(\estwth_1^\top ,\estwth_0^\top )^\top $ of $\wth^*=(\wth_1^{*\top},\wth_0^{*\top})^\top $, the desired controller $\mv \tau^*\approx -\NN(\q_{NN};\wth^*)-\mv\epsilon$ with bounded approximation error $\mv \epsilon\in\R^2$, can be approximated as follows:
\begin{equation}
    \mv \tau := -\NN({\q_{NN}};\estwth)
    .
    \label{eq. control law}
\end{equation}
For further sections, let $\idealNN:=\NN({\q_{NN}};\idealwth)$ and $\idealact :=\act({\idealwV}_0^{\top}{\q_{NN}})$, and let $\estNN:={\NN}({\q_{NN}};\estwth)$, $\estact :=\act(\estwV_0^{\top}{\q_{NN}})$ and $\estact' := \pptfrac{\estact}{(\estwV_0^\top \q_{NN})}$.

Using \eqref{eq. system dynamics 2}, \eqref{eq. desired control}, and \eqref{eq. control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi:=(\tilde {\q}^\top ,\tilde {\mv z}^\top)^\top \in\R^{2n}$ as follows:
\begin{equation}
    \dot{\mv \xi} 
    = 
    \mm A_\xi{\mv \xi}+\mm B_\xi(\NN^*-\estNN+\mv\epsilon)
    ,
\end{equation}
and 
\begin{equation}
    \mm A_\xi := 
    \begin{bmatrix}
        -{k_q} \mm I_{n} &\mm I_{n}
        \\
        -\mm I_{n}& -{k_z} \mm I_{n}
    \end{bmatrix}
    ,\ 
    \mm B_\xi := 
    \begin{bmatrix}
        \mm 0_{n\times n}\\\widehat{\mm M}^{-1}
    \end{bmatrix}.
\end{equation}

@@

\color{red}
    As discussed in Section \ref{sec:intro}, the boundedness of the weights should be considered to prevent excessively large control inputs and system instability.
\color{black}
For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ i\in\{0,1\}$.
The control problem can be reformulated into a constrained optimization problem as follows:
\begin{equation}
    \begin{matrix}
        \min_{{\estwth}} \ J(\mv \xi;{\estwth})
        :=
        \tfrac{1}{2}
        \mv \xi^\top \mm \Lambda \mv \xi
        \\ \\
        \begin{aligned}
        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal I 
        = 
        \{\theta_0,\theta_1\}
        ,
        \end{aligned}
    \end{matrix}
\end{equation}
where $\mm \Lambda=\mm \Lambda^\top >0$ denotes the weighting matrix.
In this optimization problem, $\mv \xi$ is considered a predefined parameter.
The corresponding Lagrangian function is defined as
\begin{equation}
    L(
        \mv \xi,
        {\estwth},
        [\lambda_j]_{j\in\mathcal I}
    )
    := 
    J(\mv \xi;{\estwth})
    +
    \textstyle\sum_{j\in\mathcal I} \lambda_jc_j({\estwth})
    .
\end{equation}
% where $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
To solve the dual problem $\min_{{\estwth}} \max_{[\lambda_j]_{j\in\mathcal I}}  L$, the adaptation law is derived as follows:
\begin{subequations}
    \begin{align}
            \ddtt {{\estwth}}
            &
            =
            -\alpha 
            \pptfrac{L}{{\estwth}}
            =-\alpha 
            \left(
                \pptfrac{J}{{\estwth}}
                +
                \textstyle\sum_{j\in\mathcal{I}}
                \lambda_j 
                \pptfrac{c_j}{\estwth}
            \right),
        \label{eq. adaptation law th}
            \\
            \ddtt\lambda_j
            & 
            = 
            \beta_j
            \pptfrac{L}{\lambda_j} 
            = 
            \beta_j c_j ,
            \quad\quad\quad\quad      \      
            \forall j\in\mathcal I,
        \label{eq. adaptation law L}
            \\
            \lambda_j 
            & 
            = 
            \max(\lambda_j,0) ,
        \label{eq. adaptation law L max}
    \end{align}
    \label{eq. adaptation laws}
\end{subequations}
where arguments of $L$ are suppressed for brevity, and $\alpha\in\R_{>0}$ and $\beta_j\in\R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
\color{red}
% The Eq.~\eqref{eq. adaptation law L max} is analog to using an active set $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ in constrained optimization theory which excludes terms of satisfied constraints in adaptation law.
\color{black}

@@

The dynamics of $\mv \xi$ can be represented as
\begin{equation}    
    \ddtt {\mv\xi} = \mm A_\xi\mv \xi +\mm B_\xi
    (
        -\estwV_1^\top \estact+\mv w(t)
    )
    ,
\end{equation}
where $\mv w(t):= {\idealwV}_1^{\top}\idealact+\mv \epsilon$ is a lumped residual term, which is bounded as $\norm{\mv  w(t)}\le \bar w< 0$ since $\norm{\idealwth_1},\norm{\idealact}$ and $\norm{\mv\epsilon}$ are bounded.
The dynamics of ${\mm \eta}_1$ and ${\estwth}_1$ are represented as
\begin{equation}
    \begin{aligned}
        \ddtt{\mm \eta}_1 =
        & 
        \mm A_\xi {\mm \eta}_1 -\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )
        ,
        \\
        \ddtt{{\estwth}}_1 =
        & -\alpha 
        (
            {\mm \eta}_1^\top 
            \mm \Lambda
            \mv\xi
            +
            2\lambda_{\theta_1} {\estwth}_1
        )
        .
    \end{aligned} 
\end{equation}
According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $-\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )$ is bounded.

@@

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{System model parameters.}
    \centering
    \begin{tabular}{c c c c c }
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_1, m_2$ & Mass of link    & 23.902 (kg) & 3.88 (kg) \\
    \hline
    $l_1, l_2$  & Length of link   & 0.45 (m) & 0.45 (m) \\
    \hline
    $l_{c1}, l_{c2}$ & COM of link  & 0.091 (m) & 0.048 (m) \\
    \hline
    $\theta_1, b_2$   & Viscous coefficient  &  2.288 (Nms) & 0.172 (Nms) \\
    \hline
    $f_{c1}, f_{c2}$  & Friction coefficient &  7.17 (Nm) & 1.734 (Nm) \\
    \hline
    \end{tabular}
    \label{table: system parameters}
\end{table}

@@

The control laws of all three controllers were the same as those defined in \eqref{eq. control law}.
The adaptation law of NAC-L2 is derived by adding the squared weight term $\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$ to the objective function such that $J_{L_2} = J+\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$, where $\lambda\in\R_{>0}$ denotes the $L_2$ coefficient.
The adaptation law obtained via the gradient descent method is subsequently adjusted by adding a stabilizing term $-\alpha\lambda{\estwth}$ as follows:
\begin{equation} 
    \ddtt{{\estwth}} = 
    \pptfrac{J_{L_2}}{\estwth}
    =-\alpha
    \left(
        \pptfrac{J}{\estwth}
        +
        \lambda{\estwth}
    \right)
    .
    \label{eq. adap L2}
\end{equation}
Note that this adaptation law derived based on $L_2$-regularization method in deep learning is inherently the same as the $\sigma$-modification in adaptive control theory, which adds the term $-\alpha\sigma{\estwth}$, where $\sigma\in\R_{>0}$.
For NAC-eMod, similar to the $\sigma$-modification, the stabilizing function $-\alpha\rho\norm{\tilde{\mv z}}{\estwth}$ is added to the adaptation law as follows:
\begin{equation}
    \ddtt{{\estwth}} = -\alpha
    \left(
        \pptfrac{J}{\estwth}
        +
        \rho\norm{\tilde {\mv z}}{\estwth}
        ,
    \right)
    \label{eq. adap eMod}
\end{equation}
where $\rho\in\R_{>0}$ denotes the $\epsilon$-modification coefficient.
By $\norm{\tilde {\mv z}}$, the stabilizing function proportionally increases as the tracking error $\tilde {\mv z}$ increases.
Therefore, the adaptation attempts to reduce the tracking error mainly without the effect of the stabilizing function if the tracking error is sufficiently regulated.
The adaptation law of NAC-CO is presented in \eqref{eq. adaptation laws}.
Owing to the stabilizing functions, the weights of NAC-L2 and NAC-eMod are biased since the stabilizing functions drive the weights toward the origin.

All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\widehat{\mm M}=\mm I_2$ and $\mm \Lambda=\text{diag}([5,1,15,15])$.
The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
\color{red}    
    The validity of the selected number of nodes were demonstrated through experiments 
\color{black}
The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{NN}=[\qd^\top ,1]^\top $.
For NAC-CO, the parameters of the weight norm constraints were set as $\bar\theta_0=10$ and $\bar\theta_1=20$.
The sampling time of the simulation and the simulation termination time were set to $T_s=100\ \mu\mathrm{s}$ and $T=10\ \mathrm{s}$, respectively.

@@

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Quantitative comparison of square root of tracking ISE.}
    \centering
    \begin{tabular}{c c c c }
    \hline
     & \textbf{NAC-L2}\!&\!\textbf{NAC-eMod}\!&\!\textbf{NAC-CO} (proposed) 
     \\
     \hline
    \hline 
    Maximum\!&\!$11.1753\!\times\!10^{-3}$\!&\!$0.5603\!\times\!10^{-3}$\!&\!$0.3439\!\times\!10^{-3}$\!\\
    \hline
    % Upper quartile  & $1.7284$e-3 & $0.5566$e-3 & $0.3261$e-3 \\
    % \hline
    Median\!&\!$0.5898\!\times\!10^{-3}$\!&\!$0.5519\!\times\!10^{-3}$\!&\!$0.3240\!\times\!10^{-3}$\!\\
    \hline
    % Lower quartile  & $0.5533$e-3 & $0.5470$e-3 & $0.3238$e-3 \\
    % \hline
    Minimum\!&\!$0.5434\!\times\!10^{-3}$\!&\!$0.5434\!\times\!10^{-3}$\!&\!$0.3235\!\times\!10^{-3}$\!\\
    \hline
    \end{tabular}
    \label{table: error norm}
\end{table}
